Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-31 Grassmannian_cells.tex
Section 3.2 edits (almost done...)

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

The next result establishes some basic homological properties of the translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \ses{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\] 
    \item For any $I'\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\ne0$ if and only if $I'\subset I$, in which case
      \[\Hom(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^{I'},\tilde P_{m+1}^I)=0.\]
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
    \item We have $\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0$.
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.(3).
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  The first claim of part (2) is an immediate consequence of Lemma~\ref{le:unique morphisms}.(1) together with Theorem~\ref{covering}.
  For the second claim of part (2), we apply $\Hom(-,\tilde P_{m+1}^I)$ to the sequence \eqref{ses1} for $I'$.

  Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering}

  The first part of (4) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
  For the second part of (4), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
  Then taking into account Lemma~\ref{le:homdecomposition} part (4), we get the isomorphism
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (4).

  Part (5) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} and then using parts (1) and (2).
\end{proof}

@@

\begin{remark}
  We should point out that the case $m=2$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
  Indeed, recall from the proof of Lemma~\ref{le:special subrepresentations} that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\] 
  If we factor out the image of this morphism from $\tau\tilde P_3^I$, the remaining representation is a direct sum of the simple injective representations corresponding to the vertices $(2,\alpha_i^{-1})$ for $i\in I$, $i\ne j$.
  Note that these disappear after reflecting at all sources.
\end{remark}

@@

%Note that by Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $I\subsetneq J\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
%\[\ses{\bigoplus_{i\in J\setminus I}\tilde P_{m,i}}{\tilde P_m^I}{\tilde P_{m+1}^J}.\]

\newpage
\sayD{Notation changes still needed after this point.}

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering for general $m$.

For $\uj=(j_1,\ldots,j_{n-1})\in I_{n-1}$, let $j^c\in \{1,\ldots,n\}$ be the unique element with $j^c\neq j_i$ for $i=1,\ldots,n-1$ and define $\uj^c=(j^c)\in I_1$.

\begin{definition}
  Let ${\bf j}:=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$ be a sequence with $\underline{j_1}\in I_{n-1}$, $\underline{j_2},\ldots,\underline{j_{r-1}}\in I_{n-2}$ and $\underline{j_r}\in I_s$ with $s\leq n-2$. Define $j_1^c$ as before.
 We say that ${\bf j}$ is admissible if 
$$ j_{k,i}\neq j_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,i=1,\ldots,n-2\text{ and for }i=1,\ldots,s\text{ if }k=r$$
where $j_{k}^c\in\{1,\ldots,n\}$ for $2\leq k\leq r-1$ is recursively defined as the unique element satisfying $j_k^c\neq j_{k,i}$ for $i=1,\ldots,n-2$ and $j_k^c\neq j_{k-1}^c$. 
\end{definition}

%For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
%\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$. We define the admissible sequence $\delta {\bf j}$ by
\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$. We obtain the following analogue of Lemma \ref{cor:truncated preprojective isomorphism}.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$. Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
		for $k=1,\ldots,r$.
  \end{enumerate}
\end{lemma}

\begin{definition}
  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge1$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
  \begin{enumerate}
    \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_l:=(I'_{l-1})^c\cup I_l$ for $1\le l\le k$ satisfy $(I'_{l-1})^c\cap I_l=\varnothing$ for $1\le l\le k$.
      In particular, we have $|I'_l|=n-1$ for $0\le l\le k-1$.
  \end{enumerate}
  Any sequence consisting of a single nonempty subset $\bfI=(I_1)$ will also be considered admissible.
  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_1)=(I_1^c)$.
\end{definition}

In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
That is, taking $\varepsilon=(-1)^{m+1}$ we have an exact sequence
\[\ses{\bigoplus_{i\in I} \tilde P_{m,w\alpha_i^\varepsilon}}{\tilde P_{m+1,w}}{\tilde P_{m+1,w}^I}.\]
These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
We adopt similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}$ for $0\le l\le k-1$.
      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a sequence of surjections
      \[\tilde P_{m+1}\onto\tilde P_{m+1}^{I'_0}\onto\tilde P_{m,i_0}^{I'_1}\onto\tilde P_{m-1,(i_0,i_1)}^{I'_2}\onto\cdots\onto P_{m+1-k,\ui}^{I'_k}.\]
      the truncated preprojective representation
      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_{k+1}}\]
      is a quotient of $\tilde P_{m+1}$ with $\Hom(\tilde P_{m+1},\tilde P_{m+1-k}^\bfI)\cong\CC$.
      These quotients  
  \item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
    \[\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}\]
    is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$.
    Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
    \[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
    for $k=1,\ldots,r$.
  \end{enumerate}
\end{lemma}
\begin{proof}

For part (1), we consider the following commutative diagram, where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0 \\
  0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[u] & \tilde P_{m,j}\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]

>>>>

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\xonto}[1]{\xrightarrow{#1}\!\!\!\!\!\to}
\newcommand{\ses}[3]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar[r] & #3 \ar[r] & 0}}
\newcommand{\sesm}[4]{\xymatrix{0\ar[r] & #1\ar[r] & #2\ar^{#4}[r] & #3 \ar[r] & 0}}
%\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

The next result establishes some basic homological properties of the translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \sesm{\bigoplus_{i\in I} \tilde P_{m,i}}{\tilde P_{m+1}}{\tilde P_{m+1}^I}{\pi_{m+1}^I}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

In what follows, we will need to understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.

\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC.\] 
    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subset I$, in which case
      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.(3).
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).

  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).
\end{proof}

@@

\begin{remark}
  \label{rem:special case}
  We should point out that the case $m=2$ of Lemma~\ref{le:special subrepresentations} is rather special because it is the only one for which the unique morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is not surjective.
  Indeed, recall from the proof of Lemma~\ref{le:special subrepresentations} that the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
  \begin{equation}
    \label{eq:special case}
    (2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).
  \end{equation}
  If we factor out the image of this morphism from $\tau\tilde P_3^I$, the remaining representation is a direct sum of the simple injective representations corresponding to the vertices $(2,\alpha_i^{-1})$ for $i\in I$, $i\ne j$.
  Note that these disappear after reflecting at all sources.
\end{remark}

@@

The next step is to introduce notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
\begin{definition}
  For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
  A sequence of subsets $\bfI=(I_0,I_1,\ldots,I_k)$, $k\ge1$, in $\{1,\ldots,n\}$ is \emph{admissible} if the following hold:
  \begin{enumerate}
    \item $|I_0|=n-1$ and $|I_l|=n-2$ for $1\le l\le k-1$;
    \item the sets $I'_l$ defined recursively by $I'_0=I_0$ and $I'_{l+1}:=(I'_l)^c\cup I_{l+1}$ for $0\le l\le k$ satisfy $(I'_l)^c\cap I_{l+1}=\varnothing$ for $0\le l\le k$.
  \end{enumerate}
  Here we take $I_{k+1}=\varnothing$.

  Given an admissible sequence $\bfI$, define a new admissible sequence $\delta\bfI=(I'_1,I_2,\ldots,I_k)$, where we set $\delta(I_0)=(I'_1)$.
\end{definition}

In the same way as for the preprojective lifts $\tilde P_{m+1}$, $m\ge1$, we can define truncated preprojectives $\tilde P_{m+1,w}^I$ of any translate $\tilde P_{m+1,w}$, where $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
That is, taking $\varepsilon=(-1)^{m+1}$ we have an exact sequence
\[\ses{\bigoplus_{i\in I} \tilde P_{m,w\alpha_i^\varepsilon}}{\tilde P_{m+1,w}}{\tilde P_{m+1,w}^I}.\]
These quotients are unique in the sense that $\Hom(\tilde P_{m+1,w},\tilde P_{m+1,w}^I)=\CC$ for all $w\in W_n$ and $I\subsetneq\{1,\ldots,n\}$.
We adopt similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.

By Lemma~\ref{le:properties}.(1), we can quotient out the lifted preprojectives successively, i.e.\ for any proper subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ we have a short exact sequence
\[\sesm{\bigoplus_{i\in I\setminus J}\tilde P_{m,i}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}{\pi_{m+1}^{J,I}}.\]
For any sequence of proper subsets $K\subsetneq J\subsetneq I\subsetneq\{1,\ldots,n\}$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
For $w\in W_n$, we write $\pi_{m+1,w}^{I,J}:\tilde P_{m+1,w}^I\to\tilde P_{m+1,w}^J$ for the translated morphism with similar notation for truncated preprojectives $\tilde P_{m+1-k,\ui}^I$ for $\ui\in A_1^{(k)}$ and $I\subsetneq\{1,\ldots,n\}$.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item For $I\subsetneq\{1,\ldots,n\}$ with $|I|=n-1$ and $I^c=\{j\}$, we have an isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,j}^{I^c}=\tilde P_{m,j}/\tilde P_{m-1,(j,j)}.\]
    \item Consider an admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and write $(I'_l)^c=\{i_l\}=:J_l$ for $0\le l\le k-1$.
      For $\ui=(i_0,\ldots,i_{k-1})$, there exists a commutative diagram:
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C70pt{\tilde P_{m+1} \ar^(.4){\pi_{m+1}^{I_0}}[d] & \ar[l] \tilde P_{m,i_0} \ar_(.4){\pi_{m,i_0}^{J_0}}[dl]\ar^(.4){\pi_{m,i_0}^{I'_1}}[d] & \ar[l] \tilde P_{m-1,(i_0,i_1)} \ar_(.4){\pi_{m-1,(i_0,i_1)}^{J_1}\;}[dl]\ar^(.4){\pi_{m-1,(i_0,i_1)}^{I'_2}}[d] & \ar[l] \ar[dl] \cdots & \ar[l] \tilde P_{m+1-k,\ui} \ar_(.4){\pi_{m+1-k,\ui}^{J_{k-1}}\;}[dl]\ar^(.4){\pi_{m+1-k}^{I'_k}}[d]\\
        \tilde P_{m+1}^{I'_0}\ar^{\pi_{m,i_0}^{J_0,I'_1}}[r] & \tilde P_{m,i_0}^{I'_1}\ar^{\pi_{m-1,(i_0,i_1)}^{J_1,I'_2}}[r] & \tilde P_{m-1,(i_0,i_1)}^{I'_2}\ar^(.6){\pi_{m-2,(i_0,i_1,i_2)}^{J_2,I'_3}}[r] & \cdots\ar^{\pi_{m+1-k,\ui}^{J_{k-1},I'_k}}[r] & \tilde P_{m+1-k,\ui}^{I'_k}}
      \end{equation}
      where the composed map $\pi_{m+1}^\bfI:\tilde P_{m+1}\to\tilde P_{m+1-k,\ui}^{I'_k}$ is unique up to scaling and therefore we write
      \[\tilde P_{m+1}^\bfI:=\tilde P_{m+1-k,\ui}^{I'_k}.\]
      These truncated preprojective representations satisfy 
      \[\tilde P_{m+1}^\bfI=\tilde P_{m,i_0}^{\delta\bfI}=\cdots=\tilde P_{m+1-k,\ui}^{\delta^k\bfI}.\]
  \end{enumerate}
\end{lemma}
\begin{proof}

For part (1), we consider the following commutative diagram, where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r]&\tau\tilde P_{m+1}=\tilde P_{m-1} \ar[r]\ar[d] & \tilde P_{m,j}\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
  0\ar[r] &\bigoplus_{i\in I}\tilde P_{m,i}\ar[r] &  \tilde P_{m+1}\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
